---
title: "Example R markdown file"
author: "Simina M. Boca"
output: html_document
always_allow_html: true
---

# Header 
## Header 2
### Header 3
#### Header 4
##### Header 5

This chunk gives some general settings for the whole document. You can change them in 
individual chunks.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include=TRUE, fig.path="figures/")
```

Can use _italics_ (also like *this*) or **bold** font. Can also include some
math text, like $\alpha = 0.05, \bar{X} = 1/n\sum_{i=1}^n X_i$.
Look for more tips [here](https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)! 

## Make some plots!

Let's generate some numbers and make a histogram! Don't need to name chunks but this can make it easier to pinpoint bugs.
```{r hist}
set.seed(88759)
x <- rnorm(1000)

hist(x, col="grey", main = "1000 standard normal draws")
```

In order to make it easier to find the plot, change options above!

Maybe you don't want to show the code! Change echo to FALSE above if you want that to be the default or just in individual chunks:
```{r hist_t_dist, echo=TRUE}
set.seed(88759)
t_df_3 <- rt(1000, df=3)

hist(t_df_3, col="grey", main = "1000 draws from t distribution with 3 df")
```

Save the values you generated:
```{r save_x_t}
save(list=c("x","t_df_3"), file="../objs/example_objs.RData")
```

## Make some tables!
```{r kable}
library(kableExtra)
kable(table(round(t_df_3)))
```

Use ``styling":
```{r kable_change_res}
kable(table(round(t_df_3))) %>% kable_styling()

kable(table(round(t_df_3))) %>% kable_styling(full_width = FALSE)

```

## Can run inline code!

Can use this if you need results inline: The 0.975^th^ quantile of the standard normal distribution is
`r round(qnorm(0.975),2)` whereas for a t-distribution with 3 df it is
`r round(qt(0.975,df=3),2)`.

It's always good to end with this:
```{r}
sessionInfo()
```

